Easy as Pi: A Network Coding Raspberry Pi Testbed

### 2016-06-01 schemes.tex
Explaining SRLNC

For this method, we first calculate the amount of coding coefficients
that we will use to combine.

The second method
% The reason being that here we control the \textit{average} amount
% of nonzero coefficients, but not the exact value for each coded packet. Therefore,
% we may have some cases where we have more or less packets combined. A second
% implementation in Kodo considers doing something more clever.

As is shown in \eqref{eq:sparse_coded_packet2}, that implementation
proved faster for low densities \textbf{reference?}. It is best expressed as:
%
\begin{align} \label{eq:sparse_coded_packet2}
    C_i  &= \bigoplus_{j=1}^{\floor{\text{Binom}(g,d)}} v_{im} \otimes P_{m} ,\
    %L \subseteq \{1,\dots,g\}: |L|=k ,\
    \forall i \in [1,g] ,\
    v_{ij} > 0
\end{align}
where
$m = \text{choice}(\{1,\dots,g\}, \text{size}=k, \text{replace}=\text{False})$.
\fxnote{Can this be represented smarter?}

>>>>

For this method, we first calculate the amount of coding coefficients
that we will use to combine. To do it so, a random number $\mathbb{N}$
of the original packets is used to produce a coded packet. For our case,
$\mathbb{N}$ is binomially distributed with parameters $g$ for the number
of trials and $d$ for its success probability, e.g. $\mathbb{N} \sim
Binomial(g,d)$. However, when sampling from this distribution, the case
$\mathbb{N} = 0$ occurs with a non-zero probability. In order to handle
this special case, our implementation considers
$\mathbb{K} = \max(1,\mathbb{N})$ as the final amount of packets to be
mixed together. In this way, we always ensure that at least one packet is
encoded.

The only caveat is that the case of $\mathbb{K} = 1$ occurs slightly
more often than in the original distribution, but for the
considered density range in this method it is depreciable
\textbf{Same reference here}. Then, once the distribution number of packets
to mix as been defined, we create a subset $\mathcal{C}$ of size $k$

a coded packetas is shown in
\eqref{eq:sparse_coded_packet2}, that implementation
proved faster for low densities \textbf{reference?}. It is best expressed as:
%
\begin{align} \label{eq:sparse_coded_packet2}
    C_i  &= \bigoplus_{j=1}^{\floor{\text{Binom}(g,d)}} v_{im} \otimes P_{m} ,\
    %L \subseteq \{1,\dots,g\}: |L|=k ,\
    \forall i \in [1,g] ,\
    v_{ij} > 0
\end{align}
where
$m = \text{choice}(\{1,\dots,g\}, \text{size}=k, \text{replace}=\text{False})$.
\fxnote{Can this be represented smarter?}
